---
title: "Homework Week 1"
author: "Rachel LaBella"
date: "September 8, 2016"
output: html_document
---
**Question 1**
```{r vector, echo=TRUE}
my_vec<-runif(100, min=0, max=100)
str(my_vec)
summary(my_vec)
```

Str function tells me that my vector has 100 randomly sorted numbers in it.
Summary lets me know that my minimum number is 1.727, my average is 48.170, and my max is 98.308.  
Str lists the numbers in a random assortment while summary answers specific questions about your vector like the mean, min, and max.  

**Question 2**

``` {r histogram, echo=TRUE}
hist(my_vec)
```

My histogram shows me which set of numbers are occuring with what frequencies in my vector.  

The help document about hist states that the height of the rectangle is proportional to the number of points falling in the cell. 

**Question 3**

``` {r cars, echo=TRUE}
data(mtcars)
class(mtcars)
str(mtcars)
summary(mtcars)
```

Class tells me that the mtcars is classified as a data frame.
Str shows me that the data frame consists of 32 rows and 11 columns.
There are 11 different variables (columns) for each of the 32 data points or rows.  

Summary shows the minimum, 1st quartile, median, mean, 3rd quartile, and max data points for each column or variable.  

There are 352 data points total. Each of the variables has a different data range. 

**Question 4**

The data frame consisted of Motor Trend Car Road Tests. The data was extracted from the 1974 *Motor Trend* magazine and the variables were different aspects of car design and performance. 

**Question 5**

I have not yet begun to work towards a project. I have been working on Ron's mussel distribution research these past few days but I am still just on the surface of knowing the full details of the project.   

Personally I am really interested in fish and sharks. There are a lot of papers and resources out on White shark migration especially in Cape Cod in the past 5 years. Greg Skomal does all of this research through Ocearch out of Woods Hole. I would love to do my project on analyzing their migratory patters if there is enough information to draw from. I can also pull in other species that summer in the Northeast and winter in  the south.   

Here are a few questions that I may be able to answer:  
Are warming waters causing early shark migrations?  
Are stricter fishing practices increasing shark populations?


